\LARGE \bf The Battle for Filter Supremacy: A Comparative Study of the Multi-State Constraint Kalman Filter and the Sliding Window Filter

### 2014-12-31 Report/project_report.tex
Added note about notation and other little edits

In this work, we compare and contrast two modern solutions: the Sliding Window Filter (SWF), the Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA}.
The MSCKF is a hybrid approach that combines the accuracy of the SWF with the computational efficiency of an Extended Kalman Filter (EKF).
The MSCKF has recently been used to achieve accurate, online position tracking onboard a smartphone \cite{Li:2013:ICRA}, while the SWF has been applied to planetary landing \cite{Sibley:2010:JFR}.
We present an experimental comparison of the SWF and MSCKF using different datasets consisting of IMU and camera data with accurate ground truth for both sensor motion and landmark positions.
In order to provide context for the MSCKF and SWF, we first outline the EKF approach to the SLAM problem.

@@

\section{Extended Kalman Filter (EKF)} \label{sec:EKF}
In the Extended Kalman Filter (EKF) solution, vehicle poses and feature positions are simultaneously estimated at each time step by augmenting the filter state with feature positions.
This technique, sometimes referred to as EKF-SLAM, attempts to track pose changes and create a globally consistent map of features by recursively updating the state as new measurements become available.
%Features are commonly parametrized as three-dimensional vectors and are initialized using two-view geometry, but alternative parametrization and initialization schemes exist \cite{Sola:2011:IJCV}.
%In this paper we consider only the three-dimensional parametrization and two-view initialization scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sliding Window Filter (SWF)} \label{sec:SWF}
In contrast to EKF-SLAM, the aim of the Sliding Window Filter (SWF) is not to construct a globally consistent map, but rather to estimate a vehicle's motion by optimizing a sliding window of vehicle poses and feature positions.
The optimization problem in the SWF is typically solved as a non-linear least squares problem using Gauss-Newton (GN) optimization over a sliding window of $K$ poses observing $M$ features: 
\begin{equation}
\Vec{x} := \bbm \Vec x_0^T & \hdots & \Vec x_K^T & {\Vec {p}_G^{f_1G \hspace{0.3em} T}} & \hdots & {\Vec {p}_G^{f_MG \hspace{0.3em} T}} \ebm ^T.
\end{equation}
The optimization applies an update, $ \delta \Vec{x}^*$, by solving the linear system:
\begin{equation}
(\Vec H^T \Vec T ^{-1} \Vec H ) \delta \Vec{x}^*  = - \Vec{H}^T\Vec{T}^{-1}\Vec{e}(\bar{\Vec{x}})
\end{equation}
The matrix $\Vec{H}$ is given by (showing non-zero blocks only)
\begin{equation}
\mathbf{H} = \left[\begin{array}{cccccc}
 -\Vec H_{\Vec x, 1} & \Vec 1 & & &   \\ 
 & -\Vec G_{\Vec x, 1} &  &   -\Vec G_{\Vec f, 1} \\ \hline
 & \ddots & \ddots & \vdots  \\  \hline
 & -\Vec H_{\Vec x, K} & \Vec 1 & \\ 
 & & -\Vec G_{\Vec x, K} &  -\Vec G_{\Vec f, K}   \\  
\end{array}\right], 
\end{equation}
where
\begin{align}
\Vec G_{\Vec x, k} &= \bbm \Vec G_{\Vec x, k}^1 & \hdots & \Vec G_{\Vec x, k}^M \ebm ^T
\\[0.5em]
\Vec G_{\Vec{x}, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}}
    \bbm -\Vec C_{CG} \Vec C_{IG,k} \\[0.5em] \Vec C_{CG} (\Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec p_{G,k}^{IG} ) )^\times  \ebm ^T
\\[0.5em]
\Vec G_{\Vec f, k} &= \underbrace{\bbm \Vec G_{\Vec f, k}^1 & & \\ & & \Vec G_{\Vec f, k}^2 & \\ & & \vdots &  \\ & & & \Vec G_{\Vec f, k}^M \ebm}_{\text{$j$th block column position given by feature ID $j\in[1,M]$}} \\[0.5em]
\Vec G_{\Vec f, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} \Vec C_{CI} \Vec C_{IG,k}
\end{align}
with
\begin{equation}
\bar{\Vec p}_{C_k}^{f_j C_k} := \bbm x \\ y \\ z \ebm = \Vec C_{CI} \left( \Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec{p}_{G,k}^{IG} )   - \Vec p_I^{CI} \right),
\end{equation}

\begin{equation}
\pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} = \frac{1}{z^2} \bbm f_u z & 0 & - f_u x \\  0 & f_v z & -f_v y \ebm.
\end{equation}

The weight matrix $\Vec T$ is given by:
\begin{equation}
\Vec{T} := \text{diag} \left\{ \Vec{T}_1,\hdots,\Vec{T}_K \right\}
\end{equation}
where
\begin{equation}
\Vec{T}_k := \bbm \Vec H_{\Vec w, k} \Vec Q_k \Vec H_{\Vec w, k}^T & \Vec 0 \\
\Vec 0 & \Vec G_{\Vec n, k} \Vec R_k \Vec G_{\Vec n, k}^T \ebm,
\end{equation}
and $\Vec R_k$, $\Vec Q_k$ are observation and motion model noise covariances, and $\Vec G_{\Vec n, k}$, $\Vec H_{\Vec w, k}$ are the observation and motion model Jacobians with respect to the noise.

The update is performed repeatedly until convergence (in this work we use the criterion $|\delta \Vec{x}^*| < 10^{-3} $).
An important advantage of the SWF is that its computational cost depends on the number of features in the current window rather than the number of features in the entire map.
By varying the spatial or temporal extent of the sliding window, the computational cost of the algorithm can be tailored to fit a given compute envelope, which makes the algorithm suitable for online operation over paths of arbitrary length.

@@

\subsection{MSCKF State Covariance Propagation}
With reference to the partitions defined in (\ref{eq:covariance}), we compute the predicted camera-camera and IMU-camera state covariances as follows:
\begin{align}
    \hat{\Vec{P}}^-_{CC,k+1} &= \hat{\Vec{P}}_{CC,k} \\
    \hat{\Vec{P}}^-_{IC,k+1} &= \boldsymbol{\Phi}\left(t_k + T, t_k \right) \hat{\Vec{P}}_{IC,k}
\end{align}
where $T$ is the IMU sampling period, and the state transition matrix $\boldsymbol{\Phi}\left(t_k + T, t_k \right)$ is obtained by integrating
\begin{align} \label{eq:statetransition}
    \dot{\boldsymbol{\Phi}}\left(t_k + \tau, t_k \right) &= \Vec{F} \boldsymbol{\Phi}\left(t_k + \tau, t_k \right), \tau\in\left[0,T\right]
\end{align}
with the initial condition $\boldsymbol{\Phi}\left(t_k, t_k \right) = \Vec{1}_{12}$.

We obtain the predicted IMU-IMU state covariance $\hat{\Vec{P}}^-_{II,k+1}$ by integrating
\begin{align} \label{eq:imucovar}
    \dot{\hat{\Vec{P}}}_{II}\left(t_k  + \tau \right) &= \Vec{F} \hat{\Vec{P}}_{II}\left(t_k  + \tau \right) 
                 + \hat{\Vec{P}}_{II}\left(t_k  + \tau \right) \Vec{F}^T \notag \\ 
                & + \Vec{G} \Vec{Q}_I \Vec{G}^T, \tau\in\left[0,T\right]
\end{align}
with the initial condition $\hat{\Vec{P}}_{II}\left(t_k\right) = \hat{\Vec{P}}_{II,k}$.

\subsection{Feature Position Estimation}
When a tracked feature $f_j$ is selected for a state update, the MSCKF estimates its position $\hat{\Vec{p}}_G^{f_j G}$ using an inverse-depth least-squares Gauss-Newton optimization. 
The procedure takes as input $N$ camera poses and $N$ sets of ``ideal'' pixel measurements, where ``ideal'' means that the pixel measurements have been corrected for the camera intrinsics:
\begin{align}
\hat{\Vec{z}}_i^{(j)} &= \bbm u'_i & v'_i \ebm ^T = \bbm (u_i - c_u)/f_u & (v_i - c_v)/f_v \ebm ^T.
\end{align}
We initialize the optimization by estimating the position of feature $f_j$ in camera frame $C_1$ using a linear least-squares method with measurements from the first two camera frames, $C_1$ and $C_2$:
\begin{align}
\hat{\Vec{p}}_{C_1}^{f_j C_1} := \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & \hat{Z}^{(j)}_{C_1} \ebm ^T = \lambda \boldsymbol{\rho}_{C_1}^{f_j}
\end{align}
where
\begin{align}
\boldsymbol{\rho}_{C_i}^{f_j} &:= \frac{1}{\sqrt{u'^2_i + v'^2_i + 1}}\bbm u'_i & v'_i & 1\ebm^T
\end{align}
and
\begin{align}
\lambda &= \left[(\Vec A^T \Vec A)^{-1} \Vec A^T \hat{\Vec{p}}_{C_1}^{C_2 C_1} \right]_1
\end{align}
with
\begin{align}
\Vec A &:= \bbm \boldsymbol{\rho}_{C_1}^{f_j} & -\boldsymbol{\rho}_{C_2}^{f_j} \ebm.
\end{align}

We can express the feature position in camera frame $C_i$ in terms of its position in camera frame $C_1$ as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i} .
\end{align}
By forming the vector
\begin{align}
\hat{\Vec{y}} &:= \bbm \alpha & \beta & \gamma \ebm^T := \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T ,
\end{align}
we can define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm .
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
and the linear least-squares system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1^{(j)}, \hdots, \Vec{R}_N^{(j)} \right\}
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.
The Jacobian elements are given by
\begin{align}
\frac{\partial \Vec e}{\partial \alpha} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_1 \\[0.5em]
                        -\frac{\partial h_2}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \beta} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \gamma} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_2 \ebm
\end{align}
where
\begin{align}
\frac{\partial h_1}{\partial \alpha} &= C_{11}, & \frac{\partial h_1}{\partial \beta} &= C_{12}, & \frac{\partial h_1}{\partial \gamma} &= \hat{x}_{C_i}^{C_1 C_i} \notag \\
\frac{\partial h_2}{\partial \alpha} &= C_{21}, & \frac{\partial h_2}{\partial \beta} &= C_{22}, & \frac{\partial h_2}{\partial \gamma} &= \hat{y}_{C_i}^{C_1 C_i} \\
\frac{\partial h_3}{\partial \alpha} &= C_{31}, & \frac{\partial h_3}{\partial \beta} &= C_{32}, & \frac{\partial h_3}{\partial \gamma} &= \hat{z}_{C_i}^{C_1 C_i} \notag .
\end{align}

\subsection{MSCKF State Correction Equations}
Now that we have estimated the positions of any features to be used in the state update, we can apply the corresponding motion constraints to the window of poses from which each feature was observed.
We begin by forming the exteroceptive measurement error corresponding to an observation $\Vec{z}_i^{(j)}$ of feature $f_j$ from the $i^\text{th}$ camera pose $C_i$ in the window:
\begin{align} \label{eq:residual_def}
    \Vec{r}_i^{(j)} &:= \Vec{z}_i^{(j)} - \hat{\Vec{z}}_i^{(j)}
\end{align}
where
\begin{align}
    \hat{\Vec{z}}_i^{(j)} &= \frac{1}{\hat{Z}^{(j)}_{C_i}} \bbm \hat{X}^{(j)}_{C_i} & \hat{Y}^{(j)}_{C_i} \ebm ^T
\end{align}
with 
\begin{align}
    \hat{\Vec{p}}_{C_i}^{f_j C_i} &= \bbm \hat{X}^{(j)}_{C_i} & \hat{Y}^{(j)}_{C_i} & \hat{Z}^{(j)}_{C_i} \ebm ^T = \hat{\Vec{C}}_{C_i G} \left( \hat{\Vec{p}}_G^{f_j G} - \hat{\Vec{p}}_G^{C_i G} \right).
\end{align}

>>>>

In this work, we compare and contrast two modern solutions: the Sliding Window Filter (SWF) and the Multi-State Constraint Kalman Filter (MSCKF) \cite{Mourikis:2006:TechReport,Mourikis:2007:ICRA}.
The MSCKF is a hybrid estimator that combines the accuracy of the SWF with the computational efficiency of an Extended Kalman Filter (EKF).
The MSCKF has recently been used to achieve accurate, online position tracking onboard a smartphone \cite{Li:2013:ICRA}, while the SWF has been applied to planetary landing \cite{Sibley:2010:JFR}.
We present an experimental comparison of the SWF and MSCKF using different datasets consisting of IMU and camera data with accurate ground truth for both sensor motion and landmark positions.
In order to provide context for the MSCKF and SWF, we first outline the EKF approach to the SLAM problem.

@@

\section{Extended Kalman Filter (EKF)} \label{sec:EKF}
In the Extended Kalman Filter (EKF) solution, vehicle poses and feature positions are simultaneously estimated at each time step by augmenting the filter state with feature positions.
This technique, sometimes referred to as EKF-SLAM, attempts to track vehicle motion and create a globally consistent map of features by recursively updating the state as new measurements become available.
%Features are commonly parametrized as three-dimensional vectors and are initialized using two-view geometry, but alternative parametrization and initialization schemes exist \cite{Sola:2011:IJCV}.
%In this paper we consider only the three-dimensional parametrization and two-view initialization scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sliding Window Filter (SWF)} \label{sec:SWF}
In contrast to EKF-SLAM, the aim of the Sliding Window Filter (SWF) is not to construct a globally consistent map, but rather to estimate a vehicle's motion by optimizing a sliding window of vehicle poses and feature positions.
The optimization problem in the SWF is typically solved as a non-linear least squares problem using Gauss-Newton (GN) optimization over a sliding window of $K$ poses $\Vec x_{k\in[1,K]}$ observing $M$ features $f_{j\in[1,M]}$: 
\begin{equation}
\Vec{x} := \bbm \Vec x_0^T & \hdots & \Vec x_K^T & {\Vec {p}_G^{f_1G \hspace{0.3em} T}} & \hdots & {\Vec {p}_G^{f_MG \hspace{0.3em} T}} \ebm ^T.
\end{equation}
In our notation, $\Vec p^{BA}_A$ is the vector from the origin of frame $\mathcal{F}_A$ to the origin of frame $\mathcal{F}_B$ expressed in $\mathcal{F}_A$, and $\Vec C_{BA}$ is the rotation matrix from $\mathcal{F}_A$ to $\mathcal{F}_B$.

The optimization applies an update, $ \delta \Vec{x}^*$, by solving the linear system:
\begin{equation}
(\Vec H^T \Vec T ^{-1} \Vec H ) \delta \Vec{x}^*  = - \Vec{H}^T\Vec{T}^{-1}\Vec{e}(\bar{\Vec{x}})
\end{equation}
The matrix $\Vec{H}$ is given by (showing non-zero blocks only)
\begin{equation}
\mathbf{H} = \left[\begin{array}{cccccc}
 -\Vec H_{\Vec x, 1} & \Vec 1 & & &   \\ 
 & -\Vec G_{\Vec x, 1} &  &   -\Vec G_{\Vec f, 1} \\ \hline
 & \ddots & \ddots & \vdots  \\  \hline
 & -\Vec H_{\Vec x, K} & \Vec 1 & \\ 
 & & -\Vec G_{\Vec x, K} &  -\Vec G_{\Vec f, K}   \\  
\end{array}\right], 
\end{equation}
where
\begin{align}
\Vec G_{\Vec x, k} &= \bbm \Vec G_{\Vec x, k}^1 & \hdots & \Vec G_{\Vec x, k}^M \ebm ^T
\\[0.5em]
\Vec G_{\Vec{x}, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}}
    \bbm -\Vec C_{CG} \Vec C_{IG,k} \\[0.5em] \Vec C_{CG} (\Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec p_{G,k}^{IG} ) )^\times  \ebm ^T
\\[0.5em]
\Vec G_{\Vec f, k} &= \underbrace{\bbm \Vec G_{\Vec f, k}^1 & & \\ & & \Vec G_{\Vec f, k}^2 & \\ & & \vdots &  \\ & & & \Vec G_{\Vec f, k}^M \ebm}_{\text{$j$th block column position given by feature ID $j\in[1,M]$}} \\[0.5em]
\Vec G_{\Vec f, k}^j &= \pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} \Vec C_{CI} \Vec C_{IG,k}
\end{align}
with
\begin{equation}
\bar{\Vec p}_{C_k}^{f_j C_k} := \bbm x \\ y \\ z \ebm = \Vec C_{CI} \left( \Vec C_{IG,k} (\Vec{p}_G^{f_j G} - \Vec{p}_{G,k}^{IG} )   - \Vec p_I^{CI} \right),
\end{equation}

\begin{equation}
\pd{\Vec g}{ \Vec p}\Bigr|_{\bar{\Vec p}_{C_k}^{f_j C_k}} = \frac{1}{z^2} \bbm f_u z & 0 & - f_u x \\  0 & f_v z & -f_v y \ebm.
\end{equation}
The weight matrix $\Vec T$ is given by:
\begin{equation}
\Vec{T} := \text{diag} \left\{ \Vec{T}_1,\hdots,\Vec{T}_K \right\}
\end{equation}
where
\begin{equation}
\Vec{T}_k := \bbm \Vec H_{\Vec w, k} \Vec Q_k \Vec H_{\Vec w, k}^T & \Vec 0 \\
\Vec 0 & \Vec G_{\Vec n, k} \Vec R_k \Vec G_{\Vec n, k}^T \ebm,
\end{equation}
and $\Vec R_k$, $\Vec Q_k$ are observation and motion model noise covariances, and $\Vec G_{\Vec n, k}$, $\Vec H_{\Vec w, k}$ are the observation and motion model Jacobians with respect to the noise.
The update is performed repeatedly until convergence (in this work we use the criterion $|\delta \Vec{x}^*| < 10^{-3} $).

An important advantage of the SWF is that its computational cost depends on the number of features in the current window rather than the number of features in the entire map.
By varying the spatial or temporal extent of the sliding window, the computational cost of the algorithm can be tailored to fit a given compute envelope, which makes the algorithm suitable for online operation over paths of arbitrary length.

@@

\subsection{MSCKF State Covariance Propagation}
With reference to the partitions defined in (\ref{eq:covariance}), we compute the predicted camera state covariances and IMU-camera cross-correlations as follows:
\begin{align}
    \hat{\Vec{P}}^-_{CC,k+1} &= \hat{\Vec{P}}_{CC,k} \\
    \hat{\Vec{P}}^-_{IC,k+1} &= \boldsymbol{\Phi}\left(t_k + T, t_k \right) \hat{\Vec{P}}_{IC,k}
\end{align}
where $T$ is the IMU sampling period, and the state transition matrix $\boldsymbol{\Phi}\left(t_k + T, t_k \right)$ is obtained by integrating
\begin{align} \label{eq:statetransition}
    \dot{\boldsymbol{\Phi}}\left(t_k + \tau, t_k \right) &= \Vec{F} \boldsymbol{\Phi}\left(t_k + \tau, t_k \right), \tau\in\left[0,T\right]
\end{align}
with the initial condition $\boldsymbol{\Phi}\left(t_k, t_k \right) = \Vec{1}_{12}$.

We obtain the predicted IMU state covariance $\hat{\Vec{P}}^-_{II,k+1}$ by integrating
\begin{align} \label{eq:imucovar}
    \dot{\hat{\Vec{P}}}_{II}\left(t_k  + \tau \right) &= \Vec{F} \hat{\Vec{P}}_{II}\left(t_k  + \tau \right) 
                 + \hat{\Vec{P}}_{II}\left(t_k  + \tau \right) \Vec{F}^T \notag \\ 
                & + \Vec{G} \Vec{Q}_I \Vec{G}^T, \tau\in\left[0,T\right]
\end{align}
with the initial condition $\hat{\Vec{P}}_{II}\left(t_k\right) = \hat{\Vec{P}}_{II,k}$.

\subsection{Feature Position Estimation}
When a tracked feature $f_j$ is selected for a state update, the MSCKF estimates its position $\hat{\Vec{p}}_G^{f_j G}$ using an inverse-depth least-squares Gauss-Newton optimization. 
The procedure takes as input $N$ camera poses and $N$ sets of ``ideal'' pixel measurements, where ``ideal'' means that the pixel measurements have been corrected for the camera intrinsics:
\begin{align}
\hat{\Vec{z}}_i^{(j)} &= \bbm u'_i & v'_i \ebm ^T = \bbm (u_i - c_u)/f_u & (v_i - c_v)/f_v \ebm ^T.
\end{align}
We initialize the optimization by estimating the position of feature $f_j$ in camera frame $C_1$ using a linear least-squares method with measurements from the first two camera frames, $C_1$ and $C_2$:
\begin{align}
\hat{\Vec{p}}_{C_1}^{f_j C_1} := \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & \hat{Z}^{(j)}_{C_1} \ebm ^T = \lambda \boldsymbol{\rho}_{C_1}^{f_j}
\end{align}
where
\begin{align}
\boldsymbol{\rho}_{C_i}^{f_j} &:= \frac{1}{\sqrt{u'^2_i + v'^2_i + 1}}\bbm u'_i & v'_i & 1\ebm^T
\end{align}
is the direction of the ray emanating from camera $C_i$ along which feature $f_j$ must lie, and
\begin{align}
\lambda &= \left[(\Vec A^T \Vec A)^{-1} \Vec A^T \hat{\Vec{p}}_{C_1}^{C_2 C_1} \right]_1
\end{align}
with
\begin{align}
\Vec A &:= \bbm \boldsymbol{\rho}_{C_1}^{f_j} & -\boldsymbol{\rho}_{C_2}^{f_j} \ebm.
\end{align}

We can express the feature position in camera frame $C_i$ in terms of its position in camera frame $C_1$ as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i} .
\end{align}
By forming the vector
\begin{align}
\hat{\Vec{y}} &:= \bbm \alpha & \beta & \gamma \ebm^T := \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T ,
\end{align}
we can define three functions
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm
\end{align}
and rewrite the camera measurement error as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm .
\end{align}
The linear least-squares system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1^{(j)}, \hdots, \Vec{R}_N^{(j)} \right\}
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.
The Jacobian elements are given by
\begin{align}
\frac{\partial \Vec e}{\partial \alpha} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_1 \\[0.5em]
                        -\frac{\partial h_2}{\partial \alpha} h_3 + \frac{\partial h_3}{\partial \alpha} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \beta} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \beta} h_3 + \frac{\partial h_3}{\partial \beta} h_2 \ebm
\\[0.5em]
\frac{\partial \Vec e}{\partial \gamma} &= 
    \frac{1}{h_3^2} \bbm -\frac{\partial h_1}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_1 \\[0.5em] 
                        -\frac{\partial h_2}{\partial \gamma} h_3 + \frac{\partial h_3}{\partial \gamma} h_2 \ebm
\end{align}
where
\begin{align}
\frac{\partial h_1}{\partial \alpha} &= C_{11}, & \frac{\partial h_1}{\partial \beta} &= C_{12}, & \frac{\partial h_1}{\partial \gamma} &= \hat{x}_{C_i}^{C_1 C_i} \notag \\
\frac{\partial h_2}{\partial \alpha} &= C_{21}, & \frac{\partial h_2}{\partial \beta} &= C_{22}, & \frac{\partial h_2}{\partial \gamma} &= \hat{y}_{C_i}^{C_1 C_i} \\
\frac{\partial h_3}{\partial \alpha} &= C_{31}, & \frac{\partial h_3}{\partial \beta} &= C_{32}, & \frac{\partial h_3}{\partial \gamma} &= \hat{z}_{C_i}^{C_1 C_i} \notag .
\end{align}

\subsection{MSCKF State Correction Equations}
Now that we have estimated the positions of any features to be used in the state update, we can apply the corresponding motion constraints to the window of poses from which each feature was observed.
We begin by forming the exteroceptive measurement error corresponding to an observation $\Vec{z}_i^{(j)}$ of feature $f_j$ from camera pose $C_i$:
\begin{align} \label{eq:residual_def}
    \Vec{r}_i^{(j)} &:= \Vec{z}_i^{(j)} - \hat{\Vec{z}}_i^{(j)}
\end{align}
where
\begin{align}
    \hat{\Vec{z}}_i^{(j)} &= \frac{1}{\hat{Z}^{(j)}_{C_i}} \bbm \hat{X}^{(j)}_{C_i} & \hat{Y}^{(j)}_{C_i} \ebm ^T
\end{align}
with 
\begin{align}
    \hat{\Vec{p}}_{C_i}^{f_j C_i} &= \bbm \hat{X}^{(j)}_{C_i} & \hat{Y}^{(j)}_{C_i} & \hat{Z}^{(j)}_{C_i} \ebm ^T = \hat{\Vec{C}}_{C_i G} \left( \hat{\Vec{p}}_G^{f_j G} - \hat{\Vec{p}}_G^{C_i G} \right).
\end{align}

If we linearize (\ref{eq:residual_def}) about the estimates for the camera pose and feature position, we obtain an estimate of the exteroceptive measurement error
\begin{align}
    \Vec{r}_i^{(j)} &\simeq \Vec{H}_{\Vec{x}, i}^{(j)} \widetilde{\Vec{x}}_i + \Vec{H}_{f, i}^{(j)} \widetilde{\Vec{p}}_G^{f_j G} + \Vec{n}_i^{(j)}
\end{align}
where $\Vec{H}_{\Vec{x}, i}^{(j)}$ and $\Vec{H}_{f, i}^{(j)}$ are the Jacobians of the measurement of feature $f_j$ from camera pose $C_i$ with respect to the filter state and the position of the feature, respectively.
These are given by
\begin{align}
    \Vec{H}_{\Vec{x}, i}^{(j)} &= \bbm \Vec{0} & \Vec{J}^{\left(j\right)}_i \left(\hat{\Vec{p}}_{C_i}^{f_j C_i}\right)^\times & -\Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G} & \Vec{0} \ebm \\
    \Vec{H}_{f, i}^{(j)} &= \Vec{J}^{\left(j\right)}_i \hat{\Vec{C}}_{C_i G}
\end{align}
where the left $\Vec{0}$ in $\Vec{H}_{\Vec{x}, i}^{(j)}$ has dimension $2\times\left(12+6\left(i-1\right)\right)$, the right $\Vec{0}$ has dimension $2\times6\left(N-i\right)$, and
\begin{align}
    \Vec{J}^{\left(j\right)}_i &= \frac{1}{\left(\hat{Z}^{(j)}_{C_i}\right)^2}
    \bbm \hat{Z}^{(j)}_{C_i} & 0 & -\hat{X}^{(j)}_{C_i} \vspace{0.5em} \\
             0 & \hat{Z}^{(j)}_{C_i} & -\hat{Y}^{(j)}_{C_i}
    \ebm .
\end{align}
$\Vec{n}_i^{(j)}$ is a zero-mean Gaussian noise term with covariance matrix $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.
